### 2020-12-06 paper/localpsf.tex
more edits to intro

For background on product-convolution approximations, we recommend reading the following papers: [CITES]. In [CITE], Escande and Weiss explored the idea of approximating linear operators from scattered impulse responses using a product-convolution scheme of the same form as \eqref{eq:product_convolution}. In our previous work [CITE MY PAPER], we choose the point locations with an adaptive grid. However,

@@

Let $\overline{\Omega}$ be the closure of $\Omega$, and let $C(\overline{\Omega})$ be the space of continuous functions mapping $\overline{\Omega}\rightarrow \mathbb{R}$. The action of $\mathcal{A}$ is extended to distributions $\mu:C\left(\overline{\Omega}\right) \rightarrow \mathbb{R}$ via the formula
\begin{equation*}
	\langle\mathcal{A},\mu\rangle(w) := \int_\Omega w(y) \mu\left(A(y, \cdot)\right) dy, 
\end{equation*}
where $A(y,\cdot)$ is the function $x \mapsto A(y,x)$. This is derived formally as follows:
\begin{align*}
	\langle\mathcal{A},\mu\rangle(w) &= \int_\Omega \int_\Omega w(y) A(y,x) \textrm{``} \mu(x) \textrm{''} dx dy \\
	&= \int_\Omega w(y) \int_\Omega A(y,x) \textrm{``} \mu(x) \textrm{''} dx \\
	&= \int_\Omega w(y) \mu\left(A(y,\cdot)\right) dx.
\end{align*}
For example, the delta distribution $\delta_x$ is defined by $\delta_x(v) = v(x)$, and the action of $\mathcal{A}$ on $\delta_x$ is given by
\begin{equation*}
	\langle\mathcal{A},\delta_x\rangle(w)	= \int_\Omega w(y) A(y,x) dy.
\end{equation*}

>>>>

In general, product-convolution approximations are approximations of the form \eqref{eq:product_convolution}, but where $\varphi_i$ and $w_i$ may be arbitrary functions. 
For background on product-convolution approximations, we recommend reading the following excellent papers: [CITES].

In [CITE], Escande and Weiss explored the idea of approximating linear operators from scattered impulse responses using a product-convolution scheme of the same form as \eqref{eq:product_convolution}. In our previous work [CITE MY PAPER], we choose the point locations with an adaptive grid. However,

Nagy's paper: breaking domain into regular grid, using piecewise linear interpolation.

Use for approximating Hessians in PDE-constrained optimization: Georg's paper, my paper.

Getting many impulse responses at once (batching).

Geometry-aware weighting functions vs radial basis functions

@@

Let $\overline{\Omega}$ be the closure of $\Omega$, and let $C(\overline{\Omega})$ be the space of continuous functions mapping $\overline{\Omega}\rightarrow \mathbb{R}$. The action of $\mathcal{A}$ is extended to distributions $\mu:C\left(\overline{\Omega}\right) \rightarrow \mathbb{R}$ via the formula
\begin{equation*}
	\langle\mathcal{A},\mu\rangle(w) := \int_\Omega w(y) \mu\left(A(y, \cdot)\right) dy, 
\end{equation*}
where $A(y,\cdot)$ is the function $x \mapsto A(y,x)$. This is derived formally as follows:
\begin{align*}
	\langle\mathcal{A},\mu\rangle(w) &= \int_\Omega \int_\Omega w(y) A(y,x) \textrm{``} \mu(x) \textrm{''} dx dy \\
	&= \int_\Omega w(y) \int_\Omega A(y,x) \textrm{``} \mu(x) \textrm{''} dx \\
	&= \int_\Omega w(y) \mu\left(A(y,\cdot)\right) dx.
\end{align*}
For example, the delta distribution $\delta_x$ is defined by $\delta_x(v) = v(x)$, the action of $\mathcal{A}$ on $\delta_x$ is given by
\begin{equation*}
	\langle\mathcal{A},\delta_x\rangle(w)	= \int_\Omega w(y) A(y,x) dy,
\end{equation*}
and so the Riesz representation of $\langle\mathcal{A},\delta_x\rangle$ is given by $\langle\mathcal{A},\delta_x\rangle^* = A(~\cdot~,x)$. That is, $\langle\mathcal{A},\delta_x\rangle^*$ is the function $y \mapsto A(y,x)$.
